### 2025-02-28 README.Rmd
update readme files

| function:               | purpose:                                                                                                                                   |
|-----------------|-------------------------------------------------------|
| **st_bridges()**        | *Create a neighbours list, matrix, or `sf` dataframe containing a neighbours list or matrix as column "nb", while accounting for islands.* |
| **st_quickmap_nb()**    | *Check contiguities visually on map.*                                                                                                      |
| **st_check_islands()**  | *Check assignment of island contiguities in a dataframe.*                                                                                  |
| **st_manual_join_nb()** | *Make manual changes to any connections.*                                                                                                  |
| **st_manual_cut_nb()**  | *Make manual changes to any connections.*                                                                                                  |

@@

```
```{r, echo=FALSE}
uk_election$country <- case_when(uk_election$region == "Wales" ~ "Wales",
                                  uk_election$region == "Scotland" ~ "Scotland",
                                  TRUE ~ "England")
```

@@

```{r}
nbsf <- st_bridges(df = uk_election |> filter(country == "Scotland"),
                   geom_col_name = "constituency_name",
                   link_islands_k = 2)
```

@@

```{r}
nbsf <- st_bridges(df = uk_election |> filter(country == "Scotland"),
                   geom_col_name = "constituency_name",
                   link_islands_k = 2) |> 
  st_manual_cut_nb("Na h-Eileanan An Iar", "Orkney and Shetland") |> 
  st_manual_join_nb(47, 5)
```

>>>>

| function:               | purpose:                                                                                                                                   |
|-----------------|-------------------------------------------------------|
| **st_bridges()**        | *Create a neighbours list, matrix, or `sf` dataframe containing a neighbours list or matrix as column "nb", while accounting for islands.* |
| **st_quickmap_nb()**    | *Check contiguities visually on map.*                                                                                                      |
| **st_check_islands()**  | *Check assignment of island contiguities in a dataframe.*                                                                                  |
| **st_force_join_nb()** | *Enforce changes to any connections.*                                                                                                  |
| **st_force_cut_nb()**  | *Enforce changes to any connections.*                                                                                                  |

@@

```{r, echo=FALSE}
uk_election$country <- case_when(uk_election$region == "Wales" ~ "Wales",
                                  uk_election$region == "Scotland" ~ "Scotland",
                                  TRUE ~ "England")
```

@@

```{r}
nbsf <- st_bridges(df = uk_election |> filter(country == "Scotland"),
                   row_identifier = "constituency_name",
                   link_islands_k = 2)
```

@@

```{r}
nbsf <- st_bridges(df = uk_election |> filter(country == "Scotland"),
                   row_identifier = "constituency_name",
                   link_islands_k = 2) |> 
  st_force_cut_nb("Na h-Eileanan An Iar", "Orkney and Shetland") |> 
  st_force_join_nb(47, 5)
```
